A Case Study in Preserving a High Energy Physics Application

### 2014-03-07 paper.tex
add introduction to section 4 and 6

\section{One Implemention of Fine-Grained Toolkit Using Parrot}
\subsection{Working principle of Packaging Utility}

@@

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}
\subsection{Preservation Integration of Multiple Programs}

>>>>

\section{One Implemention of Fine-Grained Toolkit Using Parrot}

The section introduces our implementation of one fine-grained packaging utility based on Solution 4. With the help of one
virtual filesystem access tool, Parrot, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the experiment.

\subsection{Working principle of Packaging Utility}

@@

%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
\section{Discussion of Data and Software Preservation}

This section concludes the important lessons of data and software preservation and experiment reproduction learnt from this case study. 
The necessity of preservation integration of multiple programs, preservation granularity, how to preserve large data, how to mine data and software dependencies,
the presrvation degree of the original filesystems, the importance of investigating user access model of data and software, will be discussed.

\subsection{Preservation Integration of Multiple Programs}
